### 2014-09-10 paper/paper.Rmd
code almost done, time to move on to the language

```{r studying, fig.width=10, fig.height=12, echo = FALSE, message = FALSE, warning = FALSE}
student.luke <- student2012[,c("name","PV1MATH","PV1READ","PV1SCIE","ST57Q01")]
study.luke <- melt(student.luke,id=c("name","ST57Q01"))
studyplot <- ggplot(data = study.luke, aes(ST57Q01, value, colour=variable)) + facet_wrap(~name) + stat_smooth(se=F)
studyplot
```

```{r studyingbar, fig.width=4, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
studybar <- ggplot(data = study.luke, aes(ST57Q01) ) + geom_histogram(binwidth=4) + xlab("Hours spent studying")
studybar
```

@@

```{r par_athomebar, fig.width=10, fig.height=12, echo = FALSE, message = FALSE, warning = FALSE}
athome = student2012[,c("name", "SCHOOLID", "STIDSTD", "OECD", "PV1MATH", "PV1SCIE", "PV1READ","ST11Q01", "ST11Q02", "ST11Q03","ST11Q04", "ST11Q05", "ST11Q06")]
athome = athome %>% filter(!is.na(athome$ST11Q01) & !is.na(athome$ST11Q02))
athome$parents = NA
athome[athome$ST11Q01 == "Yes" & athome$ST11Q02 == "Yes", ]$parents = "Both"
athome[athome$ST11Q01 == "Yes" & athome$ST11Q02 == "No", ]$parents = "Mother"
athome[athome$ST11Q01 == "No" & athome$ST11Q02 == "Yes", ]$parents = "Father"
athome[athome$ST11Q01 == "No" & athome$ST11Q02 == "No", ]$parents = "Neither"
athome$parents <- factor(athome$parents, levels=c("Both", "Mother", "Father", "Neither"))
#athome$name <- reorder(athome$name,athome$PV1MATH,mean, decreasing=F)
pbarhome <- qplot(x = parents, data = athome, xlab="Parents in home") 
pbarhome
```

>>>>

```{r studying, fig.width=10, fig.height=12, echo = FALSE, message = FALSE, warning = FALSE}
student.luke <- student2012[,c("name","PV1MATH","PV1READ","PV1SCIE","ST57Q01")]
#study.luke <- melt(student.luke,id=c("name","ST57Q01"))
studyplot <- ggplot(data = student.luke, aes(ST57Q01, PV1MATH)) + facet_wrap(~name) + stat_smooth(se=F)
studyplot
```

```{r studyingbar, fig.width=4, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
studybar <- ggplot(data = student.luke, aes(ST57Q01) ) + geom_histogram(binwidth=4) + xlab("Hours spent studying")
studybar
```

@@

```{r par_athomebar, fig.width=4, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
athome = student2012[,c("name", "SCHOOLID", "STIDSTD", "OECD", "PV1MATH", "PV1SCIE", "PV1READ","ST11Q01", "ST11Q02", "ST11Q03","ST11Q04", "ST11Q05", "ST11Q06")]
athome = athome %>% filter(!is.na(athome$ST11Q01) & !is.na(athome$ST11Q02))
athome$parents = NA
athome[athome$ST11Q01 == "Yes" & athome$ST11Q02 == "Yes", ]$parents = "Both"
athome[athome$ST11Q01 == "Yes" & athome$ST11Q02 == "No", ]$parents = "Mother"
athome[athome$ST11Q01 == "No" & athome$ST11Q02 == "Yes", ]$parents = "Father"
athome[athome$ST11Q01 == "No" & athome$ST11Q02 == "No", ]$parents = "Neither"
athome$parents <- factor(athome$parents, levels=c("Both", "Mother", "Father", "Neither"))
#athome$name <- reorder(athome$name,athome$PV1MATH,mean, decreasing=F)
pbarhome <- qplot(x = parents, data = athome, xlab="Parents in home") 
pbarhome
```
